### 2024-03-26 doc/sections/mav-syntax.tex
Tiny changes
Tiny change

Inference rules:
\begin{displaymath}
  \begin{array}{l@{\;\vInfer\;}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
    \vP\vParr\vDual\vP
     & \vUnit
     & \RuleLabel{axiom}
    \\
    \vUnit
     & \vP\vTens\vDual\vP
     & \RuleLabel{cut}
    \\
    \vUnit\vWith\vUnit
     & \vUnit
     & \RuleLabel{tidy}
    \\
    (\vP\vTens\vQ)\vParr\vR
     & \vP\vTens(\vQ\vParr\vR)
     & \RuleLabel{switch}
    \\
    (\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)
     & (\vP\vParr\vR)\vSeq(\vQ\vParr\vS)
     & \RuleLabel{sequence}
    \\
    \vP\vPlus\vQ
     & \vP
     & \RuleLabel{left}
    \\
    \vP\vPlus\vQ
     & \vQ
     & \RuleLabel{right}
    \\
    (\vP\vWith\vQ)\vParr\vR
     & (\vP\vParr\vR)\vWith(\vQ\vParr\vR)
     & \RuleLabel{external}
    \\
    (\vP\vSeq\vQ)\vWith(\vR\vSeq\vS)
     & (\vP\vWith\vR)\vSeq(\vQ\vWith\vS)
     & \RuleLabel{medial}
  \end{array}
\end{displaymath}

We write $\vEquiv$ for invertible inference rules, \ie $\vP\vEquiv\vQ$ means $\vP\vInfer\vQ$ and $\vQ\vInfer\vP$.

We write $\vInfer*$ for the reflexive, transitive closure of $\vInfer$.

@@

\begin{displaymath}
  \begin{array}{l@{\;\vInfer\;}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
    \vNeg\va\vParr\vPos\va
     & \vUnit
     & \RuleLabel{Axiom}
  \end{array}
\end{displaymath}

>>>>

Inference rules:
\begin{displaymath}
  \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
    \vP\vParr\vDual\vP
     & \vInferFrom
     & \vUnit
     & \RuleLabel{axiom}
    \\
    \vUnit
     & \vInferFrom
     & \vP\vTens\vDual\vP
     & \RuleLabel{cut}
    \\
    \vUnit\vWith\vUnit
     & \vInferFrom
     & \vUnit
     & \RuleLabel{tidy}
    \\
    (\vP\vTens\vQ)\vParr\vR
     & \vInferFrom
     & \vP\vTens(\vQ\vParr\vR)
     & \RuleLabel{switch}
    \\
    (\vP\vSeq\vQ)\vParr(\vR\vSeq\vS)
     & \vInferFrom
     & (\vP\vParr\vR)\vSeq(\vQ\vParr\vS)
     & \RuleLabel{sequence}
    \\
    \vP\vPlus\vQ
     & \vInferFrom
     & \vP
     & \RuleLabel{left}
    \\
    \vP\vPlus\vQ
     & \vInferFrom
     & \vQ
     & \RuleLabel{right}
    \\
    (\vP\vWith\vQ)\vParr\vR
     & \vInferFrom
     & (\vP\vParr\vR)\vWith(\vQ\vParr\vR)
     & \RuleLabel{external}
    \\
    (\vP\vSeq\vQ)\vWith(\vR\vSeq\vS)
     & \vInferFrom
     & (\vP\vWith\vR)\vSeq(\vQ\vWith\vS)
     & \RuleLabel{medial}
    \\
    \vC\vPlug\vP\vInferFrom\vC\vPlug\vQ
     & \text{if}
     & \vP\vInferFrom\vQ
     & \RuleLabel{cong}
    % \\
    % \vP\vInferFrom\vQ
    %  & \text{if}
    %  & \vP\vEquiv\vQ
    %  & \RuleLabel{equiv}
  \end{array}
\end{displaymath}

We write $\vInferFrom*$ for the reflexive, transitive closure of $\vInferFrom$.
We write $\vBiInfer$ for the symmetric core of $\vInferFrom$ and $\vBiInfer*$ for the reflexive, transitive closure of $\vBiInfer$.

@@

\begin{displaymath}
  \begin{array}{l@{\;\vInferFrom\;}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
    \vNeg\va\vParr\vPos\va
     & \vUnit
     & \RuleLabel{Axiom}
  \end{array}
\end{displaymath}
